refnx -- Neutron and X-ray reflectometry analysis in Python

### 2018-07-26 paper/manuscript.tex
PAPER: data reduction bits

\begin{figure}%
\centering
\label{fig:global_fit}%
\includegraphics[width=85mm]{./supporting_information/global_fit.png}%
%TODO: series labels on plots; delete points?;
%TODO: artefact in high q d2o fit; truncate at Q = 0/35 ?
%TODO: h2o fit isn't great about 0.20
%TODO: yaxis labels even, ylim?

@@

\begin{figure}
  \includegraphics[width=175mm]{./supporting_information/corner.png}
  \caption{Corner plot for the varying parameters of DMPC bilayers measured at three contrasts. The sampling took $\sim$13 minutes on a \SI{3.2}{GHz} quad-core computer for 30 saved steps, corresponding to 6000 samples, with the steps being thinned by a factor of 100.}
  \label{fig:corner}
\end{figure}

@@

\noindent
\textbf{gui.ipynb} - \Jupyter\ notebook used to create the GUI screenshot.\\
\textbf{lipid.ipynb} - \Jupyter\ notebook used for the lipid analysis example.\\
\textbf{lipid.pdf} - PDF view of the \Jupyter\ notebook used for the lipid analysis example.\\
\textbf{c_PLP0016596.dat}, \textbf{c_PLP0016601.dat}, \textbf{c_PLP0016607.dat} - example lipid datasets.\\
\textbf{refnx-paper.yml} - \conda\ environment file to reproduce the analysis environment in this paper.

>>>>

\begin{figure}%
\centering
\label{fig:global_fit}%
\includegraphics[width=85mm]{./supporting_information/global_fit.png}%
%TODO: series labels on plots; delete points?;
%TODO: artefact in high q d2o fit; truncate at Q = 0/35 ?
%TODO: h2o fit isn't great about 0.20

@@

\begin{figure}
  \includegraphics[width=175mm]{./supporting_information/corner.png}
  \caption{Corner plot for the varying parameters of DMPC bilayers measured at three contrasts. The sampling took $\sim$13 minutes on a \SI{3.2}{GHz} quad-core computer for 30 saved steps, corresponding to 6000 samples, with the steps being thinned by a factor of 100. A larger scale image is available in supporting information.}
  \label{fig:corner}
\end{figure}

@@

\noindent
\textbf{gui.ipynb} - \Jupyter\ notebook used to create the GUI screenshot.\\
\textbf{lipid.ipynb} - \Jupyter\ notebook used for the lipid analysis example.\\
\textbf{lipid.pdf} - PDF view of the \Jupyter\ notebook used for the lipid analysis example.\\
\textbf{corner.pdf} - larger scale image of the corner plot.\\
\textbf{c_PLP0016596.dat}, \textbf{c_PLP0016601.dat}, \textbf{c_PLP0016607.dat} - example lipid datasets.\\
\textbf{reduction.ipynb} - notebook for reducing example datasets.\\
\textbf{raw_data.zip} - raw files for the example datasets.\\
\textbf{refnx-paper.yml} - \conda\ environment file to reproduce the analysis environment in this paper.
